Dependently Typed Multi-stage Calculus

### 2019-11-21 slides/main.tex
Finished making the second draft.

\documentclass[dvipdfmx,aspectratio=169, 20pt]{beamer}
\usepackage[absolute,overlay]{textpos}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{ascmac}
\usepackage[backend=biber, style=numeric]{biblatex}
\usepackage{color}
\usepackage{mathtools}
\usepackage{url}
\usepackage{bcprules, proof}
\usepackage{xparse}
\usepackage{xspace}
\usepackage{fancybox}
\usepackage{float}
\usepackage{bcprules}
\usepackage{ebproof}
\usepackage{lscape}
\usepackage{pgfpages}

@@

    \begin{verbatim}
 val vadd-gen : Int -> (Vec -> Vec -> Vec) code
 # let vadd3 = vadd-gen 3;;
 (* vadd3 v w =                             *)
 (*   let (v, w)=(.~v, ,~w) in              *)
 (*   .< [v[0]+w[0];v[1]+w[1];v[2]+w[2]] >. *)
 val vadd3 : (Vec -> Vec -> Vec) code
 # (run vadd3) [1;2;3] [4;5;6];;
  - : Vec = [5;7;9]
    \end{verbatim}
    \note{
    }
\end{frame}

\begin{frame}[fragile]{The problem of vadd3 generated by vadd-gen}
    Runtime error occurs for wrong length vectors.
    \begin{verbatim}
    # (run vadd3) [1;2] [4;5];;
    Exception: Failure
    \end{verbatim}
    \note{
    }
\end{frame}

@@

\begin{frame}[fragile]{Types of \LTP}
    \begin{block}{Types}
    \begin{tabbing}
        \hspace{5mm} \( \tau \) \= ::= X \hspace{20mm} \= (constants) \\
        \> \( \mid \tau \to \tau \) \> (function type) \\
        \> \( \mid \TW\ \tau \) \> (code type)
        % \> \mid \Pi x:\tau.\sigma \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \)
    \end{tabbing}
    \end{block}
   \note{
    }
\end{frame}

@@

\begin{frame}[fragile]{Cross Stage Persistence (CSP)}
\end{frame}

\begin{frame}[fragile]{Types of \LMD}
    \begin{block}{Types}
    \begin{tabbing}
        \hspace{5mm} \( \tau \) \= ::= X \hspace{20mm} \= (constants) \\
        \> \( \mid \tau \to \tau \) \> (function type) \\
        \> \( \mid \TW\ \tau \) \> (code type)
        % \> \mid \Pi x:\tau.\sigma \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \)
    \end{tabbing}
    \end{block}
   \note{
    }
\end{frame}

\begin{frame}[fragile]{vadd-gen in \LMD}
    Type tells us the length of vector.
    \newcommand{\Vn}{\text{Vec}\ n}
    \newcommand{\Vt}{\text{Vec}\ 3}
    \begin{tabbing}
        \( \text{vadd-gen} : \Pi n:\I \to \TW_\alpha (\Vn \to \Vn \to \Vn) \) \\[2mm]
        \( \textbf{let}\ \text{vadd3} = \textbf{run}\ (\text{vadd-gen}\ 3);; \) \\
        \( \text{val}\ \text{vadd3} : \Vt \to \Vt \to \Vt \) \\[2mm]
    \end{tabbing}
    Now, vadd3 takes only vectors of 3 length.
    \note{
        vadd-gen is changed as follows in \LMD.
        Thanks to dependent types ...
    }
\end{frame}

\begin{frame}[fragile]{Terms of \LMD}
    \begin{block}{Terms}
        \( M ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M \mid \textbf{run}\ M \mid \TBL_\alpha M \)
    \end{block}
    \begin{itemize}
        \item \( c \): constants
            \begin{itemize}
                    \item true, false, etc.
            \end{itemize}
        \item \( \TB_\alpha M \): code value
        \item \( \textbf{run}\ M \): run a code value \( M \)
            \begin{itemize}
                \item \( \textbf{run }(\text{vadd-gen }3)\)
            \end{itemize}
    \end{itemize}
    \note{
        Then, let me explain details of \LMD. \\
        \( \TBL_\alpha M \) is not needed?
    }
\end{frame}

\begin{frame}[fragile]{Types of \LMD}
    \begin{block}{Types}
    \( \tau,\sigma ::= X \mid \Pi x:\tau.\sigma \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \)
    \end{block}
    \begin{itemize}
        \item \( X \): type-level constants 
            \begin{itemize}
                \item \( \text{Vec} \), \( \text{Int} \).
            \end{itemize}
        \item \( \Pi x:\tau.\sigma \): dependent type.
        \item \( \tau\ M \): Application of term to dependent type.
            \begin{itemize}
                \item \( \text{Vec } 3 \)
            \end{itemize}
        \item \( \TW_{\alpha} \tau \): a type of code of type \( \tau \).
            \begin{itemize}
                \item \( \text{vadd-gen 3} : \TW_\alpha (\text{Vec}\ 3 \to \text{Vec}\ 3 \to \text{Vec}\ 3) \)
            \end{itemize}
    \end{itemize}
    \note{
    }
\end{frame}

\begin{frame}[fragile]{Kinds of \LMD}
    \begin{block}{Kinds}
        \( K ::= * \mid \Pi x:\tau.K \)
    \end{block}
    \begin{itemize}
        \item \( * \): kind of proper type
            \begin{itemize}
                \item \( \text{Int} :: * \)
            \end{itemize}
        \item \( \Pi x:\tau.K \): kind dependent on term.
            \begin{itemize}
                \item \( \text{Vec} :: (\Pi x:\text{Int}.*) \)
            \end{itemize}
    \end{itemize}
    \note{
    }
\end{frame}

\begin{frame}[fragile]{Judgements of \LMD}
    \begin{itemize}
        \item \( \G \V K @ A \)
            \begin{itemize}
                \item \( K \) is a proper kind under signature \( \Sigma \) at stage \( A \).
            \end{itemize}
        \item \( \G \V \tau :: K @ A \)
            \begin{itemize}
                \item Type \( \tau \) has kind \( K \) under signature \( \Sigma \) at stage \( A \).
            \end{itemize}
        \item \( \G \V M : \tau @ A \)
        \item \( \G \V K \E K' @ A \)
            \begin{itemize}
                \item Kind \( K \) is equivalent to \( K' \) under signature \( \Sigma \) at stage \( A \).
            \end{itemize}
        \item \( \G \V \tau \E \tau' @ A \)
        \item \( \G \V M \E M' @ A \)
    \end{itemize}
    \note{
    }
\end{frame}

\begin{frame}[fragile]{What is stage\ \( A \)\ ?}
    % I copied this underwrite macro from
    % https://tex.stackexchange.com/questions/141932/how-to-write-under-an-underline.
    % \underwrite[<thickness>]{<numerator>}{<denominator>}
    \newcommand{\underwrite}[3][]{
        \genfrac{}{}{#1}{}{\textstyle #2}{\textstyle #3}
    }

    Level of nested brankets
    \begin{block}{Stages}
        \( A := \varepsilon (\text{empty}) \mid \alpha \mid A\alpha \)
    \end{block}
    \begin{center}
        \( \underbrace{(\textbf{run}\ (\TB_\alpha\ \overbrace{(2 + 3)}^{\let\scriptstyle\textstyle\substack{@\alpha}})) + 1}_{\let\scriptstyle\textstyle\substack{@\varepsilon}} \)
    \end{center}
    \note{
        Stage is a sequence of stage variables which appended to each brack triangles.
        \( \varepsilon \) means the empty sequence

        The wholes expression is a term on stage \( \varepsilon \),
        But subexpression in the brack triangle is a term on stage \( \alpha \).
    }
\end{frame}

\begin{frame}[fragile]{What is signature \( \Sigma \)\ ?}
    Signature \( \Sigma \) is a sequence of type-level constants and constant values.
    \begin{itemize}
        \item For example,
            \begin{itemize}
                \item \( \Sigma = \text{Int}::*, \text{Vec}::\Pi x:\text{Int}.*, 0:\text{Int} \)
            \end{itemize}
        \item Elements of \( \Sigma \) can be used at any stages.
    \end{itemize}
    \note{
        自然数が無限個あるというツッコミを誘発する気がする。
        後者関数が存在することにするか?
    }
\end{frame}

\begin{frame}[fragile]{Typing Rules of \LMD}
    \begin{center}
        \infrule[{\TTB}]{
            \G\V M:\tau@{A\alpha}
        }{
            \G\V\TB_{\alpha}M:\TW_{\alpha}\tau@A
        } \\[2mm]
        \infrule[{\textsc{T-App}}]{
            \G\V M:(\Pi (x:\sigma).\tau)@A \andalso
            \G\V N:\sigma@A
        }{
            \G\V M\ N : \tau[x\mapsto N]@A
        } \\[2mm]
        \infrule[{\TConst}]{
            c:\tau \in \Sigma \andalso
        }{
            \G \V c:\tau@A
        }
    \end{center}
    \begin{itemize}
        \item Terms are stage sensitive so cannot ignore stages.
        \item Constants in \( \Sigma \) can be used at any stages.
    \end{itemize}
    \note{
        Let's have a look on some typing rules.
    }
\end{frame}

\begin{frame}[fragile]{Kinding Rules of \LMD}
    \begin{center}
        \infrule[{\KTW}]{
            \G\V \tau::*@A\alpha
        }{
            \G\V\TW_\alpha \tau::*@A
        }\\[2mm]
        \infrule[{\KApp}]{
            \G\V \sigma:: (\Pi x:\tau.K)@A \andalso \G\V M:\tau@A
        }{
            \G\V \sigma\ M::K[x\mapsto M]@A
        }
        \infrule[{\KTConst}]{
            X::K \in \Sigma
        }{
            \G \V X::K@A
        }
    \end{center}
    \begin{itemize}
        \item Types are also stage sensitive.
        \item Type-level constants in \( \Sigma \) can be used at any stages.
    \end{itemize}
    \note{
        Kinding rules have something in common with typing rules.
    }
\end{frame}

\begin{frame}[fragile]{Example of Kinding Derivation}
    \renewcommand{\Vec}{\text{Vec}}
    \( \V \TB_\alpha [1,2,3] : \underbrace{\TW_\alpha (\Vec\ 3)}_{\TW_\alpha (\Vec\ 3) :: * @ \varepsilon} @ \varepsilon \) \\[2mm]
    \pause
    \( \Sigma = \Vec::\Pi x:\I.*, 0:\I, 1:\I, \cdots \)
    \begin{center}
        \footnotesize
        \begin{minipage}{0.7\hsize}
            \infer[\KTW]
            {\V \TW_\alpha (\Vec\ 3) :: * @ \varepsilon}
            {
                \infer[\KApp]
                {\V \Vec\ 3 :: * @ \alpha}
                {
                    \infer[\KTConst]
                    {\V \Vec :: \Pi x:\I.* @ \alpha}
                    {\Vec :: \Pi x:\I.* \in \Sigma}
                    \andalso
                    \infer[\TConst]
                    {\V 3 : \I @ \alpha}
                    {3 : \I \in \Sigma}
                }
            }
        \end{minipage}
    \end{center}
    We can use \Vec\ and integers at any stages.
    \note{
        The constructed type Vec 3 is stage sensitive so we cannot use at arbitrary stages
        but the elements, Vec and 3 are in the signature \( \Sigma \) and can be used at any stages.
    }
\end{frame}

\begin{frame}[fragile]{Type and Term Equality Rules of \LMD}
    \begin{center}
        \footnotesize{
            \infrule[{\QTApp}]{
                \G\V \tau \E \sigma :: (\Pi x:\rho.K)@A \andalso
                \G\V M \E N : \rho @A
            }{
                \G\V \tau\ M \E \sigma\ N :: K[x \mapsto M]@A
            } \\[2mm]
            \infrule[{\QBeta}]{
                \G,x:\sigma@A\V M:\tau@A \andalso
                \G\V N:\sigma@A
            }{
                \G\V(\lambda x:\sigma.M)\ N\E M[x\mapsto N] : \tau[x \mapsto N]@A
            } \\[2mm]
            \infrule[{\QPercent}]{
                \G\V M:\tau@{A\alpha} \andalso
                \G\V M:\tau@A
            }{
                \G\V\%_\alpha M \E M : \tau@{A\alpha}
            } \\[2mm]
            \infrule[{\textsc{T-Conv}}]{
                \G\V M:\tau@A \andalso
                \G\V \tau\equiv \sigma :: K@A
            }{
                \G\V M:\sigma@A
            }
        }
    \end{center}
    \note{
    }
\end{frame}

\begin{frame}[fragile]{Examples of Type Equality}
    \renewcommand{\V}{\text{Vec}}
    \begin{itemize}
        \item \( (\lambda x:\text{Int}.x)\ 3\E 3 \)
            \begin{itemize}
                \item From \QBeta.
            \end{itemize}
        \item \( \V\ ((\lambda x:\text{Int}.x)\ 3) \E \V\ 3 \)
            \begin{itemize}
                \item From \QTApp and \QBeta.
            \end{itemize}
        \item \( \V\ (\%_\alpha 3) \E \V\ 3 \)
            \begin{itemize}
                \item Because \( 3 \) has type \text{Int} at any stage, we can use \QPercent.
            \end{itemize}
    \end{itemize}
    \note{
        Shold I show complete derivation tree?
    }
\end{frame}

\begin{frame}[fragile]{Propaties}
    \begin{itemize}
        \item Subject Reduction
        \item Strong Normalization
        \item Confluence
        \item Progress
    \end{itemize}
    \note{
    }
\end{frame}

>>>>

\documentclass[dvipdfmx,aspectratio=169, 20pt]{beamer}
\usepackage[absolute,overlay]{textpos}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{ascmac}
\usepackage[backend=biber, style=numeric]{biblatex}
\usepackage{color}
\usepackage{mathtools}
\usepackage{url}
\usepackage{bcprules, proof}
\usepackage{xparse}
\usepackage{xspace}
\usepackage{fancybox}
\usepackage{float}
\usepackage{bcprules}
\usepackage{ebproof}
\usepackage{lscape}
\usepackage{pgfpages}
\usepackage{bm}

@@

    \begin{verbatim}
 val vadd-gen : Int -> (Vec -> Vec -> Vec) code
 # let vadd3 = vadd-gen 3;;
 val vadd3 : (Vec -> Vec -> Vec) code
 (* vadd3 v w =                             *)
 (*   let (v, w)=(.~v, ,~w) in              *)
 (*   .< [v[0]+w[0];v[1]+w[1];v[2]+w[2]] >. *)
    \end{verbatim}
    \note{
    }
\end{frame}

\begin{frame}[fragile]{The problem of vadd3 generated by vadd-gen}
    Runtime error occurs for wrong length vectors.
    \begin{verbatim}
 val vadd3 : (Vec -> Vec -> Vec) code
 # (run vadd3) [1;2;3] [4;5;6];;
 - : Vec = [5;7;9]
 # (run vadd3) [1;2] [4;5];;
 Exception: Failure
    \end{verbatim}
    \note{
    }
\end{frame}

@@

\begin{frame}[fragile]{Types of \LTP}
    \begin{block}{Types}
    \begin{tabbing}
        \hspace{5mm} \( \tau \) \= ::= X \hspace{20mm} \= (constants) \\
        \> \( \mid \TW\ \tau \) \> (code type) \\
        \> \( \mid \tau \to \tau \) \> (function type)
    \end{tabbing}
    \end{block}
   \note{
    }
\end{frame}

@@

\begin{frame}[fragile]{Cross Stage Persistence (CSP)}
    Use normal values in code values
    \begin{tabbing}
        \hspace{5mm} \= \( \textbf{let}\ \text{mul3}\ x = 2 * x\ \textbf{in} \) \\
        \> \( \TB (\% \text{mul3}\ 5) \)
    \end{tabbing}
\end{frame}

\begin{frame}[fragile]{Types of \LMD}
    \begin{block}{Types}
    \begin{tabbing}
        \hspace{5mm} \( \tau \) \= ::= X \hspace{20mm} \= (constants) \\
        \> \( \mid \TW\ \tau \) \> (code type) \\
        \> \( \bm{\mid \Pi x:\tau.\tau} \) \> (function dependent type) \\
        \> \( \bm{\mid \tau\ M} \) \> (application of term to dependent type)
    \end{tabbing}
    \end{block}
    We need CSP to use normal variables in code types.
    \begin{itemize}
        \item OK  \( \Pi n: \TW (\text{Vec}\ \%n) \)
        \item NG  \( \Pi n: \TW (\text{Vec}\ n) \)
    \end{itemize}
   \note{
    }
\end{frame}

\begin{frame}[fragile]{vadd-gen in \LMD}
    Type tells us the length of vector.
    \newcommand{\Vn}{\text{Vec}\ \%n}
    \newcommand{\Vt}{\text{Vec}\ \%3}
    \begin{tabbing}
        \hspace{5mm} \= \( \text{vadd-gen} : \Pi n:\I \to \TW (\Vn \to \Vn \to \Vn) \) \\[2mm]
        \> \( \textbf{let}\ \text{vadd3} = \text{vadd-gen}\ 3;; \) \\
        \> \( \text{val}\ \text{vadd3} : \TW (\Vt \to \Vt \to \Vt) \) \\[2mm]
    \end{tabbing}
    Now, vadd3 takes only vectors of length 3.
    \note{
        vadd-gen is changed as follows in \LMD.
        Thanks to dependent types ...
    }
\end{frame}

\begin{frame}[fragile]{Problem of vadd3}
    Hard to compose with other functions.
    \newcommand{\Vn}{\text{Vec}\ \%n}
    \newcommand{\Vpt}{\text{Vec}\ \%3}
    \newcommand{\Vt}{\text{Vec}\ 3}
    \begin{tabbing}
        \hspace{5mm} \= \( \text{val}\ \text{vadd3} : \TW (\Vpt \to \Vpt \to \Vpt) \) \\
        \> \( \text{val}\ \text{double} : \TW (\Vt \to \Vt) \) \\[2mm]
        \> \( \textbf{let}\ \text{add-double}\ v\ w = \) \\
        \> \hspace{5mm} \( \TB (\TBL\text{double}\ (\TBL \text{vadd3}\ \TBL v\ \TBL w));; \) \\
    \end{tabbing}
\end{frame}

\begin{frame}[fragile]{Solution}
    \newcommand{\Vt}{\text{Vec}\ 3}
    Introduce \QPercent.
    \begin{center}
        \infrule[{\QPercent}]{
            M \text{ is a closed term.}
        }{
            \G\vdash \%_\alpha M \E M : \tau
        }
    \end{center}
    Erase the symbol of \( \% \) under the condition.
    \begin{itemize}
        \item \( \text{Vec}\ \%3 \E \text{Vec}\ 3 \)
        \item \( \text{vadd3} : \TW (\Vt \to \Vt \to \Vt) \)
    \end{itemize}
\end{frame}

% \begin{frame}[fragile]{Terms of \LMD}
%     \begin{block}{Terms}
%         \( M ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M \mid \textbf{run}\ M \mid \TBL_\alpha M \)
%     \end{block}
%     \begin{itemize}
%         \item \( c \): constants
%             \begin{itemize}
%                     \item true, false, etc.
%             \end{itemize}
%         \item \( \TB_\alpha M \): code value
%         \item \( \textbf{run}\ M \): run a code value \( M \)
%             \begin{itemize}
%                 \item \( \textbf{run }(\text{vadd-gen }3)\)
%             \end{itemize}
%     \end{itemize}
%     \note{
%         Then, let me explain details of \LMD. \\
%         \( \TBL_\alpha M \) is not needed?
%     }
% \end{frame}

% \begin{frame}[fragile]{Types of \LMD}
%     \begin{block}{Types}
%     \( \tau,\sigma ::= X \mid \Pi x:\tau.\sigma \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \)
%     \end{block}
%     \begin{itemize}
%         \item \( X \): type-level constants 
%             \begin{itemize}
%                 \item \( \text{Vec} \), \( \text{Int} \).
%             \end{itemize}
%         \item \( \Pi x:\tau.\sigma \): dependent type.
%         \item \( \tau\ M \): Application of term to dependent type.
%             \begin{itemize}
%                 \item \( \text{Vec } 3 \)
%             \end{itemize}
%         \item \( \TW_{\alpha} \tau \): a type of code of type \( \tau \).
%             \begin{itemize}
%                 \item \( \text{vadd-gen 3} : \TW_\alpha (\text{Vec}\ 3 \to \text{Vec}\ 3 \to \text{Vec}\ 3) \)
%             \end{itemize}
%     \end{itemize}
%     \note{
%     }
% \end{frame}
%
% \begin{frame}[fragile]{Kinds of \LMD}
%     \begin{block}{Kinds}
%         \( K ::= * \mid \Pi x:\tau.K \)
%     \end{block}
%     \begin{itemize}
%         \item \( * \): kind of proper type
%             \begin{itemize}
%                 \item \( \text{Int} :: * \)
%             \end{itemize}
%         \item \( \Pi x:\tau.K \): kind dependent on term.
%             \begin{itemize}
%                 \item \( \text{Vec} :: (\Pi x:\text{Int}.*) \)
%             \end{itemize}
%     \end{itemize}
%     \note{
%     }
% \end{frame}
%
% \begin{frame}[fragile]{Judgements of \LMD}
%     \begin{itemize}
%         \item \( \G \V K @ A \)
%             \begin{itemize}
%                 \item \( K \) is a proper kind under signature \( \Sigma \) at stage \( A \).
%             \end{itemize}
%         \item \( \G \V \tau :: K @ A \)
%             \begin{itemize}
%                 \item Type \( \tau \) has kind \( K \) under signature \( \Sigma \) at stage \( A \).
%             \end{itemize}
%         \item \( \G \V M : \tau @ A \)
%         \item \( \G \V K \E K' @ A \)
%             \begin{itemize}
%                 \item Kind \( K \) is equivalent to \( K' \) under signature \( \Sigma \) at stage \( A \).
%             \end{itemize}
%         \item \( \G \V \tau \E \tau' @ A \)
%         \item \( \G \V M \E M' @ A \)
%     \end{itemize}
%     \note{
%     }
% \end{frame}
%
% \begin{frame}[fragile]{What is stage\ \( A \)\ ?}
%     % I copied this underwrite macro from
%     % https://tex.stackexchange.com/questions/141932/how-to-write-under-an-underline.
%     % \underwrite[<thickness>]{<numerator>}{<denominator>}
%     \newcommand{\underwrite}[3][]{
%         \genfrac{}{}{#1}{}{\textstyle #2}{\textstyle #3}
%     }
%
%     Level of nested brankets
%     \begin{block}{Stages}
%         \( A := \varepsilon (\text{empty}) \mid \alpha \mid A\alpha \)
%     \end{block}
%     \begin{center}
%         \( \underbrace{(\textbf{run}\ (\TB_\alpha\ \overbrace{(2 + 3)}^{\let\scriptstyle\textstyle\substack{@\alpha}})) + 1}_{\let\scriptstyle\textstyle\substack{@\varepsilon}} \)
%     \end{center}
%     \note{
%         Stage is a sequence of stage variables which appended to each brack triangles.
%         \( \varepsilon \) means the empty sequence
%
%         The wholes expression is a term on stage \( \varepsilon \),
%         But subexpression in the brack triangle is a term on stage \( \alpha \).
%     }
% \end{frame}
%
% \begin{frame}[fragile]{What is signature \( \Sigma \)\ ?}
%     Signature \( \Sigma \) is a sequence of type-level constants and constant values.
%     \begin{itemize}
%         \item For example,
%             \begin{itemize}
%                 \item \( \Sigma = \text{Int}::*, \text{Vec}::\Pi x:\text{Int}.*, 0:\text{Int} \)
%             \end{itemize}
%         \item Elements of \( \Sigma \) can be used at any stages.
%     \end{itemize}
%     \note{
%         自然数が無限個あるというツッコミを誘発する気がする。
%         後者関数が存在することにするか?
%     }
% \end{frame}
%
% \begin{frame}[fragile]{Typing Rules of \LMD}
%     \begin{center}
%         \infrule[{\TTB}]{
%             \G\V M:\tau@{A\alpha}
%         }{
%             \G\V\TB_{\alpha}M:\TW_{\alpha}\tau@A
%         } \\[2mm]
%         \infrule[{\textsc{T-App}}]{
%             \G\V M:(\Pi (x:\sigma).\tau)@A \andalso
%             \G\V N:\sigma@A
%         }{
%             \G\V M\ N : \tau[x\mapsto N]@A
%         } \\[2mm]
%         \infrule[{\TConst}]{
%             c:\tau \in \Sigma \andalso
%         }{
%             \G \V c:\tau@A
%         }
%     \end{center}
%     \begin{itemize}
%         \item Terms are stage sensitive so cannot ignore stages.
%         \item Constants in \( \Sigma \) can be used at any stages.
%     \end{itemize}
%     \note{
%         Let's have a look on some typing rules.
%     }
% \end{frame}
%
% \begin{frame}[fragile]{Kinding Rules of \LMD}
%     \begin{center}
%         \infrule[{\KTW}]{
%             \G\V \tau::*@A\alpha
%         }{
%             \G\V\TW_\alpha \tau::*@A
%         }\\[2mm]
%         \infrule[{\KApp}]{
%             \G\V \sigma:: (\Pi x:\tau.K)@A \andalso \G\V M:\tau@A
%         }{
%             \G\V \sigma\ M::K[x\mapsto M]@A
%         }
%         \infrule[{\KTConst}]{
%             X::K \in \Sigma
%         }{
%             \G \V X::K@A
%         }
%     \end{center}
%     \begin{itemize}
%         \item Types are also stage sensitive.
%         \item Type-level constants in \( \Sigma \) can be used at any stages.
%     \end{itemize}
%     \note{
%         Kinding rules have something in common with typing rules.
%     }
% \end{frame}
%
% \begin{frame}[fragile]{Example of Kinding Derivation}
%     \renewcommand{\Vec}{\text{Vec}}
%     \( \V \TB_\alpha [1,2,3] : \underbrace{\TW_\alpha (\Vec\ 3)}_{\TW_\alpha (\Vec\ 3) :: * @ \varepsilon} @ \varepsilon \) \\[2mm]
%     \pause
%     \( \Sigma = \Vec::\Pi x:\I.*, 0:\I, 1:\I, \cdots \)
%     \begin{center}
%         \footnotesize
%         \begin{minipage}{0.7\hsize}
%             \infer[\KTW]
%             {\V \TW_\alpha (\Vec\ 3) :: * @ \varepsilon}
%             {
%                 \infer[\KApp]
%                 {\V \Vec\ 3 :: * @ \alpha}
%                 {
%                     \infer[\KTConst]
%                     {\V \Vec :: \Pi x:\I.* @ \alpha}
%                     {\Vec :: \Pi x:\I.* \in \Sigma}
%                     \andalso
%                     \infer[\TConst]
%                     {\V 3 : \I @ \alpha}
%                     {3 : \I \in \Sigma}
%                 }
%             }
%         \end{minipage}
%     \end{center}
%     We can use \Vec\ and integers at any stages.
%     \note{
%         The constructed type Vec 3 is stage sensitive so we cannot use at arbitrary stages
%         but the elements, Vec and 3 are in the signature \( \Sigma \) and can be used at any stages.
%     }
% \end{frame}
%
% \begin{frame}[fragile]{Type and Term Equality Rules of \LMD}
%     \begin{center}
%         \footnotesize{
%             \infrule[{\QTApp}]{
%                 \G\V \tau \E \sigma :: (\Pi x:\rho.K)@A \andalso
%                 \G\V M \E N : \rho @A
%             }{
%                 \G\V \tau\ M \E \sigma\ N :: K[x \mapsto M]@A
%             } \\[2mm]
%             \infrule[{\QBeta}]{
%                 \G,x:\sigma@A\V M:\tau@A \andalso
%                 \G\V N:\sigma@A
%             }{
%                 \G\V(\lambda x:\sigma.M)\ N\E M[x\mapsto N] : \tau[x \mapsto N]@A
%             } \\[2mm]
%             \infrule[{\QPercent}]{
%                 \G\V M:\tau@{A\alpha} \andalso
%                 \G\V M:\tau@A
%             }{
%                 \G\V\%_\alpha M \E M : \tau@{A\alpha}
%             } \\[2mm]
%             \infrule[{\textsc{T-Conv}}]{
%                 \G\V M:\tau@A \andalso
%                 \G\V \tau\equiv \sigma :: K@A
%             }{
%                 \G\V M:\sigma@A
%             }
%         }
%     \end{center}
%     \note{
%     }
% \end{frame}
%
% \begin{frame}[fragile]{Examples of Type Equality}
%     \renewcommand{\V}{\text{Vec}}
%     \begin{itemize}
%         \item \( (\lambda x:\text{Int}.x)\ 3\E 3 \)
%             \begin{itemize}
%                 \item From \QBeta.
%             \end{itemize}
%         \item \( \V\ ((\lambda x:\text{Int}.x)\ 3) \E \V\ 3 \)
%             \begin{itemize}
%                 \item From \QTApp and \QBeta.
%             \end{itemize}
%         \item \( \V\ (\%_\alpha 3) \E \V\ 3 \)
%             \begin{itemize}
%                 \item Because \( 3 \) has type \text{Int} at any stage, we can use \QPercent.
%             \end{itemize}
%     \end{itemize}
%     \note{
%         Shold I show complete derivation tree?
%     }
% \end{frame}

\begin{frame}[fragile]{Properties}
    We proved
    \begin{itemize}
        \item Subject Reduction
        \item Strong Normalization
        \item Confluence
        \item Progress
    \end{itemize}
    \note{
    }
\end{frame}
